Methodology for Assessing the State of the Practice for Domain X

### 2020-10-12 StateOfPractice/Methodology/Methodology.tex
updated Section 6 of Methodology

\section{How to Initially Filter the Software List} \label{SecInitialFilter}
The initial list of candidate software packages should first be filtered to a manageable size. Our target is about 30 packages. We want the list to include packages that are not marked as incomplete and are at least somewhat organized and understandable. We also want the list to be a good representation of the software domain, with packages having enough in common with respect to functionality that it makes sense to compare the software. The initial list of candidate software should be filtered using the following properties:

\begin{enumerate}
	\item Restrict scope (functionality?)\pmi{elaborate on this}
	\item Can we install? \pmi{elaborate on this, copy from point below?}
	\item Available documentation - The purpose of the software and the installation and usage procedures should appear to be moderately clear or easy to find.
	\ad{What if installation or usage procedures are unavailable? I think we're measuring that if the software have installation instructions and user manuals,
	so perhaps they should be kept even if these docs are missing.}
    \pmi{How are we installing the software if such documents and procedures are missing? Should we expect users to be able to install? I did not encounter a situation where even basic installation steps were missing.}
	\item \ad{What if there are still more candidates than we need? Should we also filter out the ``older'' or ``less popular'' ones if needed? }\pmi{Good question. Let's discuss during meeting.}\pmi{meeting: add point about dropping off oldest ones, look at the point below copied from previous section}
	\item \ad{``Ideally have the latest release or source code commit within the last 5 years.'' How about this one? Do we care about the ``vintage'' software?}\pmi{I tested some software that has not been updated in about 8 years, as this software was mentioned in multiple places and looked professional. That being said, age should be noted as something that is considered along with other qualities. "Ideally the latest release or source code commit should be relatively recent, such as within the last 5 years, unless the candidate software appears to be well recommended and currently in use."}

\end{enumerate}

>>>>

\section{How to Initially Filter the Software List} \label{SecInitialFilter}
The initial list of candidate software packages should first be filtered to a manageable size. Our target is about 30 packages. We want the list to include packages that are not marked as incomplete and are at least somewhat organized and understandable. We also want the list to be a good representation of the software domain, with packages having enough in common with respect to functionality that it makes sense to compare the software. The initial list of candidate software should be filtered using the following properties sequentially:

\begin{enumerate}
	\item Scope: The functionality of the domain software should be increasingly specific.
	\item Usage: The installation procedure should appear to be clear or easy to figure out.
    \item Age: Ideally the latest release or source code commit should be relatively recent, such as within the last 5 years, unless the candidate software appears to be well recommended and currently in use.
\end{enumerate}
